### 2017-04-03 paper/evaluation.tex
pass on rq2

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
  \emph{sysstat} package to measure performance, }git to fetch
subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
Python 3.4, Bash, and R to process the data and generate plots.  All
source artifacts are publicly available for replication (on
request)\Comment{ at \Fix{create gh-pages}}.  This includes supporting
scripts (\eg, the script that test subjects and generates raw analysis
data) and the full list of projects. \Comment{, and a
  \emph{Vagrantfile} to emulate our hardware and all software
  dependencies.}

@@

\begin{itemize}
    \item \textbf{\RQA}
\end{itemize}

We considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
to evaluate prevalence of projects with costly test suites.  To
measure cost we used the following methodology. \Jbc{The following
  steps may change $\rightarrow$} Figure~\ref{fig:mvn-execution} shows
the commands used in our script to test each subject. The main loop
(lines 5-11) iterates over the list of subjects and invokes Maven at
different steps (lines 7-9) as to reduce measurement noise.  We first
compiled the source and test files (line 7), made all dependencies
available locally (line 8) and later, we ran the tests in offline mode
(line 9) to bypass package updates. After the execution, we used a
regular expression on the output log to extract the elapsed time (line
10).

Prior to running this script, we randomly selected a hundred projects
to inspect corresponding execution logs.  The goal of the inspection
was to identify tasks unrelated to testing (\eg, \emph{javadoc}
generation and static analysis) that could interfere in our
measurement.  These extra tasks were ignored from execution (lines
1-3).  Furthermore, to avoid noise from operating system events, we
configured our workstation to run only essential services.  The
machine was dedicated to our experiments and we accessed it via
SSH. In addition, we configured the \CodeIn{isolcpus} option from the
Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs to
execute our experiment and the remaining CPUs to run the operating
system. By isolating a set of virtual CPUs, we prevent
context-switching from experiment processes and OS-related
processes.\Mar{can we cite this?}

@@

We ran the test suite for each subject three times reporting their
averages.  We grouped measurements in three time ranges: tests that
run within a minute (\shortg{} group), tests that run in one to five
minutes (\medg{} group), and tests that run in five or more minutes
(\longg{} group). We based our classification from a previous work
\cite{gligoric-etal-issta2015} and added the \medg{} group due to the
variability of the time cost from subjects out of the \shortg{} group.
\Jbc{these results will be updated $\rightarrow$}
Figure~\ref{fig:rq1-boxplot} shows the time cost distribution of each
group: the \shortg{} group is the most right skewed distribution with
outliers closed to the \medg{} group and 50\% of the subjects run in
less than 15 seconds; the median from the \medg{} group is nearly two
minutes and most of the subjects run in less than four minutes; most
of the \longg{} group runs in less than 25 minutes but has outliers
that require more than 50 minutes to execute.
Figure~\ref{fig:rq1-barplot} summarizes the proportion of subjects
from each group.

@@

It is important to mention that Figure~\ref{fig:rq1-barplot}
represents a lower bound estimation for time cost because some tests
may finish earlier than expected due to existing bugs on the ongoing
revision.  From the \numSubjs{} compiled projects, \numSubjsPass{}
successfully executed all tests and \numSubjsFail{} reported test
failures.  Also, some projects may omit long-running tests on their
default execution. For instance, the project
\CodeIn{apache.maven-surefire} runs all unit tests in a few seconds in
our environment.  According to our criteria, this project would be
classified as \shortg{} but we noticed that by providing additional
parameters from the subject, the integration tests are included during
the execution.  After including the integration tests, the tests time
increases to nearly 30 minutes.  Since it would be impractical to
analyze each project, we considered only the tests executed by
default.

\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQA{}:}~\emph{We concluded that
    time-consuming regression test suites are relatively frequent in
    open-source projects given that \percentMedLongRunning{} of the
    projects are costly (\ie, \numMedLong{} projects from \medg{} and
    \longg{}).}
\end{minipage}
}
\end{center}

@@

\begin{figure}[ht]
    \centering

    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.38\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/boxplots-testcases.pdf}
      \caption{\label{fig:medtcost}Distribution of test cases per group}
    \end{subfigure}\\
    \vspace{3ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Long   &  9 & 14 & 5 \\
        Medium & 17 & 20 & 7 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}\Fix{adjust values}}    
    \end{subfigure}%

    \caption{\label{fig:time-distributions}Distribution of test case
    execution cost per project.}    
\end{figure}

\sloppy Figures~\ref{fig:medtcost} and~\ref{fig:longtcost} show the
time distribution of tests per project.  We observed that the average
median value of execution cost for a test was relatively small (dashed
horizontal red lines), namely \Fix{0.41s} for \medg{} projects and
\Fix{0.23s} for \longg{} projects.  Note that correlation between cost
of test suites and cost of their individual tests is not to be
expected.  The standard deviation ($\sigma$) associated with each
distribution was relatively low.  Figure~\ref{fig:sd} shows the number
of projects within specific ranges of $\sigma$ values.  We also
observed that projects with very high standard deviations may or may
not be indicative of monopolization of execution by a small number of
tests.  For example, the highest value of $\sigma$ occurred in project
\CodeIn{wildfly-swarm}, whose test suite was classified as
long-running.  This project contains only \Fix{65} tests, \Fix{62} of
which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
an example where test suite parallelization may not be very beneficial
as \Fix{$>$99\%} execution cost is dominated by only \Fix{3\%} of the
tests.  Without these two tests this project would have been
classified as short-running.  A closer inspection in the data
indicates that the project \CodeIn{wildfly-swarm} was an extreme case;
we did not find projects with similar characteristics of time
monopolization.  Project \CodeIn{jenkinsci.gerrit-trigger-plugin} is
also classified as long-running and has the second highest value of
$\sigma$.  For this project, however, cost is distributed more
smoothly across \Fix{529} tests, of which \Fix{119} take more than
\Fix{1s} to run.

@@

\Luis{rework this $\rightarrow$}
We considered the \numNonParallel{} subjects that do not use any
parallel mode from Section~\ref{sec:rqC-1} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent \emailsSent{} e-mails to
different developers that recently contributed to the project.
There were \emailsAnswered{} replies, and \emailsTrueAnswers{} of
those were answering the survey.

@@

>>>>

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
  \emph{sysstat} package to measure performance, }git to fetch
subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
Python 3.4, Bash, R and Ruby 2.3 to process the data and generate plots.  All
source artifacts are publicly available for replication (on
request)\Comment{ at \Fix{create gh-pages}}.  This includes supporting
scripts (\eg, the script that test subjects and generates raw analysis
data) and the full list of projects. \Comment{, and a
  \emph{Vagrantfile} to emulate our hardware and all software
  dependencies.}

@@

\begin{itemize}
    \item \textbf{\RQA}
\end{itemize}
%\Jbc{The following steps may change $\rightarrow$}

To evaluate prevalence of projects with costly test suites, we
considered the \numSubjs{} testable subjects from
Figure~\ref{fig:subjects}.  Figure~\ref{fig:mvn-execution} illustrates
the script we used to measure time.  The main loop (lines 5-11)
iterates over the list of subjects and invokes Maven multiple
times\Comment{ to isolate cost of running tests} (lines 7-9).  We
first compiled the source and test files (line 7), made all
dependencies available locally (line 8), and then we ran the tests in
offline mode to skip the package update task (line 9). After
execution, we used a regular expression on the output log to extract
the elapsed time (line 10).

Prior to running this script, we inspected Maven execution logs from a
sample inclduing a hundred projects.  The goal of this inspection step
is to find tasks unrelated to testing (\eg, \emph{javadoc} generation
and static analyses) that could interfere in our measurements.  The
tasks we found were ignored from execution (lines 1-3).  Furthermore,
to avoid noise from operating system events, we configured our
workstation to run only essential services.  The machine was dedicated
to our experiments and we accessed it via SSH. In addition, we
configured the \CodeIn{isolcpus} option from the Linux Kernel
\cite{linux-kernel} to isolate six virtual CPUs to execute our
experiment, leaving the remaining CPUs to run OS
processes~\cite{isolcpus-use}.  The rationale for this decision is to
prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared the sequential execution of tests
using Maven with JUnit's default \CodeIn{JUnitCore} runner, invoked
from the command line.  We observed that results were very similar.

%% We executed each project's test suite for
%% \Fix{5} times through Maven and directly through JUnit each project

@@

We ran the test suite for each subject three times, reporting averaged
execution times in three ranges: tests that run within a minute
(\shortg{} group), tests that run in one to five minutes (\medg{}
group), and tests that run in five or more minutes (\longg{}
group). We followed a similar methodology to group projects by time as
Gligoric~\etal{}~\cite{gligoric-etal-issta2015} in their work on
regression test selection.\Comment{ and added the \medg{} group due to
  the variability of the time cost from subjects out of the \shortg{}
  group} Figure~\ref{fig:rq1-barplot} shows the number of projects in
each group.  As it is to be expected, \longg{} and \medg{} projects do
not occur as frequently as \shortg{} projects.  However, they do ocur
in relatively high numbers.  Figure~\ref{fig:rq1-boxplot} shows cost
distribution of test suites in each group as boxplots.  The
distribution associated with the \shortg{} group is the most
unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
  group}.  The test suites in this group run in 15 or less seconds for
over 75\% of the cases.  Such scenarios constitute the majority of the
cases we analyzed.  Considering the groups \medg{} and \longg{},
however, we found many costly executions.  Nearly 75\% of the projects
from the \medg{} group take over 3.5 minutes to run and nearly 75\% of
the projects from the \longg{} group take $\sim$20 minutes to run.  We
found cases in the \longg{} group were execution takes over 50 minutes
to complete, as can be observed from the outliers (dots) in the plot.

%% the median from the
%% \medg{} group is nearly two minutes and most of the subjects run in
%% less than four minutes; most of the \longg{} group runs in less than
%% 25 minutes but has outliers that require more than 50 minutes to
%% execute.

@@

%% Figure~\ref{fig:rq1-barplot} is a lower bound estimation of cost
%% because some tests may finish earlier than expected due to existing
%% test failures in the revision we downloaded.

It is important to note that we under-estimated cost in our
experiments for two main reasons.  First, some tests may finish
earlier than expected due to observed test failures in some of the
revisions we downloaded.  From the \numSubjs{} testable projects,
\numSubjsPass{} successfully executed all tests and \numSubjsFail{}
reported some test failures.  Second, some projects may omit
long-running tests on their default execution. For instance, the
project \CodeIn{apache.maven-surefire} runs all unit tests in a few
seconds in our environment.  According to our criteria, this project
would be classified as \shortg{} but we noticed that only smoke test
run by default.  The more expensive integration and system tests are
only accessible via custom parameters.  When running the test suite
with integration tests, the testing time goes to nearly 30 minutes.
For simplicity, we considered only the tests executed by default.

\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQA{}:}~\emph{We conclude that
      time-consuming test suites are relatively frequent in
      open-source projects.  We found that \percentMedLongRunning{} of
      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
      projects) take at least 3 minutes to run and
      \percentLongRunning{} take at least 5 minutes to run.\Comment{
        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{minipage}
}
\end{center}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=.75\textwidth]{plots/boxplots-testcases.pdf}
        \caption{\label{fig:medtcost}Distribution of test cases.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Long   &  7 & 15 & 12 \\
        Medium & 22 & 19 & 7 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}Standard deviantion of test cases}
    \end{subfigure}%
    \caption{\label{fig:time-distributions}Distribution of test case
    execution cost per project.}%
\end{figure}

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of tests per project.  We observed that the average
median value of execution cost for a test was relatively small (dashed
horizontal red lines), namely 0.31s for \medg{} projects and
0.23s for \longg{} projects.  Note that correlation between cost
of test suites and cost of their individual tests is not to be
expected.  The standard deviation ($\sigma$) associated with each
distribution was relatively low.  Figure~\ref{fig:sd} shows the number
of projects within specific ranges of $\sigma$ values.  We also
observed that projects with very high standard deviations may or may
not be indicative of monopolization of execution by a small number of
tests.  For example, the highest value of $\sigma$ occurred in project
\CodeIn{uber\_chaperone}, whose test suite was classified as
medium-running.  This project contains only \Fix{65} tests, \Fix{62} of
which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
an example where test suite parallelization may not be very beneficial
as \Fix{$>$99\%} execution cost is dominated by only \Fix{3\%} of the
tests.  Without these two tests this project would have been
classified as short-running.  A closer inspection in the data
indicates that the project \CodeIn{uber\_chaperone} was an extreme case;
we did not find projects with similar characteristics of time
monopolization.  Project \CodeIn{facebookarchive\_linkbench} is
classified as long-running and has the second highest value of
$\sigma$.  For this project, however, cost is distributed more
smoothly across \Fix{529} tests, of which \Fix{119} take more than
\Fix{1s} to run.

@@

To understand why developers prefer not use parallel test execution,
we considered the \numNonParallel{} subjects that do not use any
parallel mode from Section~\ref{sec:rqC-1} (\ie{}, \medg{} and
\longg{}
projects that does not run in parallel by default) and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent \emailsSent{} e-mails to
different developers that recently contributed to the project.
There were \emailsAnswered{} replies, and \emailsTrueAnswers{} of
those were answering the survey.

@@

\Luis{these values need macro $\rightarrow$}
From the valid replies, we noticed that \Fix{55.2\%
(16/\emailsTrueAnswers{})} of developers use an external continuous
integration server to run tests, \Fix{27.6\% (8/\emailsTrueAnswers{})} run tests in the
development machine, \Fix{13.8\% (4/\emailsTrueAnswers{})} did
not specified the environment.
